```latex
\documentclass[letterpaper,10pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}
\setlength{\multicols}{2}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright
\input{glyphtounicode}
\pdfgentounicode=1
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=20pt, labelsep=10pt]
}{
  \end{itemize}
}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}
\renewcommand\labelitemi{--}

\begin{document}

\documentTitle{Khan Mohammad Shayshab Azad}{
  \href{tel:+49 15750613186}{
    \raisebox{-0.05\height} \faPhone\ +49 15750613186} ~ | ~
    \href{mailto:km.shayshab@gmail.com}{
    \raisebox{-0.15\height} \faEnvelope\ me@shayshab.xyz} ~ | ~
  \href{mailto:me@shayshab.xyz}{
    \raisebox{-0.15\height} \faEnvelope\ km.shayshab@gmail.com} ~ | ~
  \href{https://linkedin.com/in/shayshab-azad/}{
    \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/shayshab-azad} ~ | ~
  \href { https://github.com/shayshab}{
    \raisebox{-0.15\height} \faGithub \ github.com/shayshab} 
  
    \href{https://www.shayshab.xyz/}{
    \raisebox{-0.15\height} {\textbf Portfolio: }\ https://www.shayshab.xyz}{ (Access code: 2025)}
  \textbf{ Location: Berlin, Germany}
}

\section*{Professional Summary}
Marketing Professional with over five years of senior influencer marketing experience, specializing in direct-to-consumer brand engagement in the health and wellness sector. Proven ability to develop data-driven marketing strategies, manage high-performing teams, and optimize budgets for maximum ROI.

\section{Core Competencies}
\begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=120 pt]
  \item[\textbf{Influencer Marketing :}] Strategy Development, Partnership Building, Brand Advocacy
  \item[\textbf{Leadership :}] Team Mentorship, Vision Planning, Creative Empowerment
  \item[\textbf{Budget Management :}] ROI Optimization, Resource Allocation, €400K+ Budget Expertise
  \item[\textbf{Digital Platforms :}] Instagram, TikTok, YouTube, Emerging Channels
  \item[\textbf{Performance Metrics :}] KPI Integration, Analytics, Continuous Improvement
  \item[\textbf{Communication :}] English (Fluent), German (Preferred)
  \item[\textbf{Strategic Thinking :}] Commercial Impact, Data-Driven Decision Making
\end{itemize}

\section{Experience}
\headingBf{Direct-to-Consumer Brand}{Mar 2019 -- Present}
\headingIt{Head of Influencer Marketing}{Berlin, Germany}
\begin{resume_list}
  \item Developed and led influencer marketing strategies boosting brand value and commercial outcomes.
  \item Built a data-led culture within the team, integrating KPIs and optimizing influencer activities.
  \item Managed budgets over €400K monthly, ensuring efficient resource allocation for maximum impact.
  \item Scaled influencer programs across various platforms and international markets.
  \item Led and mentored a team to drive creativity, innovation, and accountability.
\end{resume_list}

\headingBf{Wellness Startup}{Jan 2017 -- Feb 2019}
\headingIt{Influencer Marketing Specialist}{}
\begin{resume_list}
  \item Executed influencer campaigns that aligned with brand mission and values.
  \item Collaborated with cross-functional teams to enhance brand storytelling and audience engagement.
  \item Analyzed campaign performance to continually refine marketing strategies.
  \item Cultivated long-term influencer partnerships through innovative content and events.
\end{resume_list}

\section{Education}
\headingBf{Berlin University of Applied Sciences (BHT)}{2025}
\headingIt{Master's in Information and Communications Engineering}{}

\section{Projects}
\begin{resume_list}
  \item Developed influencer marketing campaigns that significantly increased brand visibility and engagement.
  \item Implemented a comprehensive data analysis system to measure influencer campaign effectiveness.
\end{resume_list}

\section{Certifications}
\headingBf{Certified Digital Marketing Professional}{2025}
\headingBf{Certified Content Marketing Specialist}{2023}

\vspace{-0.5em}

\section{Awards}
\headingBf{Influencer Marketing Award \textnormal{Direct-to-Consumer Brand}}{2024}
\headingIt{Recognition for outstanding contribution to influencer marketing success.}{}

\section*{Portfolio}
For further details on my projects, campaigns, and marketing strategies, please visit my online portfolio at: \textbf{\href{https://www.shayshab.xyz/}{https://www.shayshab.xyz}} (Access Code: 2025)

\end{document}
```