\documentclass[letterpaper,10pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}
\setlength{\multicols}{2}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright
\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=20pt, labelsep=10pt]
}{
  \end{itemize}
}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}
\renewcommand\labelitemi{--}

\begin{document}

  \documentTitle{Khan Mohammad Shayshab Azad}{
    \href{tel:+49 15750613186}{
      \raisebox{-0.05\height} \faPhone\ +49 15750613186} ~ | ~
      \href{mailto:km.shayshab@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ me@shayshab.xyz} ~ | ~
    \href{mailto:me@shayshab.xyz}{
      \raisebox{-0.15\height} \faEnvelope\ km.shayshab@gmail.com} ~ | ~
    \href{https://linkedin.com/in/shayshab-azad/}{
      \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/shayshab-azad} ~ | ~
    \href { https://github.com/shayshab}{
      \raisebox{-0.15\height} \faGithub \ github.com/shayshab} 
     
      \href{https://www.shayshab.xyz/}{
      \raisebox{-0.15\height} {\textbf Portfolio: }\ https://www.shayshab.xyz}{ (Access code: 2025)}
    \textbf{ Location: Berlin, Germany}
  }

\section*{Professional Summary}
Detail-oriented Business Analyst with experience in analyzing and documenting business requirements, improving processes, and supporting the implementation of business solutions. Strong analytical skills with a focus on operational efficiency and effective stakeholder collaboration.

\section{Core Competencies}

  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=120 pt]
    \item[\textbf{Business Analysis :}] Requirements Gathering, Process Improvement, Workflow Analysis
    \item[\textbf{Project Management :}] Stakeholder Management, Agile Methodologies, Risk Assessment
    \item[\textbf{Software Tools :}] Microsoft Excel, Word, PowerPoint, Jira, Trello
    \item[\textbf{Data Analysis :}] Proficient in Data Interpretation and Reporting, Dashboard Preparation
    \item[\textbf{Communication :}] Effective Written and Verbal Communication, Report Preparation
    \item[\textbf{Problem Solving :}] Analytical and Strategic Thinking, Solution Implementation
  \end{itemize}

\section{Experience}

\headingBf{Deutsche Börse}{Mar 2024 -- Apr 2025}
\headingIt{Business Analyst}{}
\begin{resume_list}
  \item Analyzed and documented business requirements, collaborating with stakeholders to translate needs into technical specifications.
  \item Identified process improvement opportunities, providing actionable recommendations for efficiency enhancement.
  \item Assisted in developing business processes and systems, supporting executable business solutions.
  \item Prepared comprehensive reports and dashboards to communicate findings and progress to stakeholders.
  \item Coordinated with IT teams to implement process changes, ensuring alignment with business objectives.
\end{resume_list}

\vspace{-0.5em}
\headingBf{Eurex - Deutsche Börse Group}{Apr 2023 -- Feb 2024}
\headingIt{Information Security Analyst}{}
\begin{resume_list}
  \item Conducted business process modeling and requirements gathering.
  \item Assisted in implementing solutions aligned with project goals and stakeholder expectations.
  \item Monitored project progress, reporting risks and mitigation strategies to ensure project success.
  \item Collaborated with cross-functional teams to execute process improvements effectively.
\end{resume_list}

\vspace{-0.5em}
\headingBf{YAS.life(Temp Mini job)}{Oct 2023 -- Feb 2024}
\headingIt{Project Coordinator}{}
\begin{resume_list}
  \item Supported project management activities, aiding in the successful deployment of IT solutions.
  \item Automated monitoring tasks using data analysis tools, enhancing reporting accuracy and timeliness.
  \item Contributed to the development of IT documentation, ensuring knowledge sharing and procedural clarity.
\end{resume_list}

\newpage
\section{Education}

\headingBf{Berlin University of Applied Sciences (BHT)}{2025}
\headingIt{Master's in Information and Communications Engineering}{}
\begin{resume_list}
  \item Relevant Courses: Business Process Analysis, Data Analytics, Software Engineering.
  \item Ongoing Thesis: \textit{“Enhancing Business Process Efficiency through Technological Solutions”}.
\end{resume_list}

\headingBf{Green University of Bangladesh}{2020}
\headingIt{Bachelor's in Business Administration}{}
\begin{resume_list}
  \item Relevant Courses: Business Management, Project Management, Data Analysis.
\end{resume_list}

\vspace{-1em}

\section{Projects}

\begin{resume_list}
    \item Developed business process improvement strategies, resulting in a 20% efficiency gain.
    \item Implemented data visualization solutions using tools like Power BI to enhance decision-making.
    \item Conducted analysis for process optimization in project management, achieving measurable outcomes.
\end{resume_list}

\vspace{-1em}

\section{Training and Certifications}

\headingBf{Certified Business Analyst Professional (CBAP)}{2025}
\headingBf{Project Management Professional (PMP) \textnormal{PMI}}{2023}
\headingBf{Certified ScrumMaster (CSM) \textnormal{Scrum Alliance}}{2022}

\vspace{-0.5em}

\section{Awards}

\headingBf{BaHSiG Scholarship Award \textnormal{Bangladeshi Students' Association in Germany}}{2024}
\headingIt{Selected as one of eleven outstanding Bangladeshi students in Germany for academic excellence.}{}

\vspace{-0.5em}

\section*{Portfolio}

For further details on my projects, certificates, experiences, and reference letters, please visit my online portfolio at: \textbf{\href{https://www.shayshab.xyz/}{https://www.shayshab.xyz}} (Access Code: 2025)
\end{document}