\documentclass[letterpaper,10pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}
\setlength{\multicols}{2}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright
\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=20pt, labelsep=10pt]
}{
  \end{itemize}
}

\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

\renewcommand\labelitemi{--}

\begin{document}

  \documentTitle{Khan Mohammad Shayshab Azad}{
    \href{tel:+49 15750613186}{
      \raisebox{-0.05\height} \faPhone\ +49 15750613186} ~ | ~
      \href{mailto:km.shayshab@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ me@shayshab.xyz} ~ | ~
    \href{mailto:me@shayshab.xyz}{
      \raisebox{-0.15\height} \faEnvelope\ km.shayshab@gmail.com} ~ | ~
    \href{https://linkedin.com/in/shayshab-azad/}{
      \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/shayshab-azad} ~ | ~
    \href { https://github.com/shayshab}{
      \raisebox{-0.15\height} \faGithub \ github.com/shayshab} 
     
      \href{https://www.shayshab.xyz/}{
      \raisebox{-0.15\height} {\textbf Portfolio: }\ https://www.shayshab.xyz}{ (Access code: 2025)}
    \textbf{ Location: Berlin, Germany}
  }



\section*{Professional Summary}
Strategic Influencer Marketing Professional with over five years of experience in leading high-impact marketing strategies. Skilled in developing data-driven influencer campaigns, optimizing partnerships across international markets, and managing budgets to maximize ROI. Proven track record in building brand advocacy through innovative marketing and content initiatives.

   \section{Core Competencies}

  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=120 pt]
   
    \item[\textbf{Influencer Strategy:}] Campaign Development, Long-term Brand Advocacy, Content Initiatives
    \item[\textbf{Leadership & Mentorship:}] Team Building, Vision Setting, Cultivating Creativity
    \item[\textbf{Data-Driven Marketing:}] KPI Integration, Performance Analytics, Continuous Optimization
    \item[\textbf{Budget Management:}] Efficient Resource Allocation, ROI Maximization
    \item[\textbf{International Growth:}] Scaling Campaigns, Multi-channel Strategy, Cross-market Partnerships
    \item[\textbf{Professional Language Skills:}] English (Fluent), German (Intermediate)
  \end{itemize}

\section{Experience}

\headingBf{Eurex - Deutsche Börse Group}{Apr 2023 -- Feb 2024}
\headingIt{Marketing Strategist}{}
\begin{resume_list}
  \item Developed influencer marketing strategies that enhanced brand presence on Instagram, TikTok, and YouTube.
  \item Guided a team in creating innovative content campaigns, fostering an environment of creativity and scalability.
  \item Managed and optimized a significant marketing budget, ensuring alignment with brand goals and KPI outcomes.
  \item Expanded partnership programs across new platforms and regions, increasing brand footprint significantly.
\end{resume_list}

\vspace{-0.5em}
\headingBf{YAS.life (Freelance)}{Oct 2023 -- Feb 2024}
\headingIt{Influencer Marketing Consultant}{}
\begin{resume_list}
  \item Led influencer partnerships that drove brand engagement and consumer loyalty.
  \item Implemented analytics to track performance, leading to data-informed strategic improvements.
  \item Cultivated relationships with key influencers, aligning campaign efforts with company values and mission.
\end{resume_list}

\vspace{-0.5em}
\headingBf{Decoders Squad}{May 2019 -- Apr 2021}
\headingIt{Head of Marketing Partnerships}{}
\begin{resume_list}
  \item Spearheaded international influencer marketing tactics, scaling brand impact in targeted markets.
  \item Facilitated performance-driven marketing strategies by integrating comprehensive data analysis.
  \item Established a structured leadership approach, fostering a culture of accountability and innovation.
\end{resume_list}

\section{Education}

\headingBf{Berlin University of Applied Sciences (BHT)}{2025}
\headingIt{Master's in Marketing and Communications}{}
\begin{resume_list}
  \item Relevant Courses: Strategic Marketing, Digital Media, Brand Management.
\end{resume_list}

\vspace{-1em}

\section{Projects}

\begin{resume_list}
    \item Developed a strategic influencer marketing framework for a direct-to-consumer brand, resulting in a 40% increase in engagement.
    \item Designed a cross-platform campaign for product launches, ensuring alignment with brand ethos and maximizing reach.
    \item Spearheaded a digital transformation initiative to embed KPI-driven decision-making processes firmly within marketing operations.
\end{resume_list}

\vspace{-1em}

\section{Certifications}

\headingBf{Certified Digital Marketing Leader}{2023}
\headingBf{Advanced Influencer Marketing Certification}{2022}
\headingBf{Strategic Brand Management Specialist}{2021}

\vspace{-0.5em}

\section{Training}
\headingBf{Digital Marketing Analytics \textnormal{Coursera}}{2024}
\headingBf{Leadership in Marketing \textnormal{LinkedIn Learning}}{2023}
\headingBf{Influencer Marketing Strategies \textnormal{Udemy}}{2022}

\vspace{-0.5em}

\section{Awards}

\headingBf{Excellence in Influencer Marketing \textnormal{Marketing Awards Berlin}}{2023}
\headingIt{Recognized for outstanding achievement in influencer marketing strategy and execution.}{}

\vspace{-0.5em}

\section*{Portfolio}

For further details on my projects, certificates, experiences, and reference letters, please visit my online portfolio at: \textbf{\href{https://www.shayshab.xyz/}{https://www.shayshab.xyz}} (Access Code: 2025)
\end{document}