Based on your current CV, here is a tailored application for the position of Head of Influencer Marketing and Partnerships at Zazu Digital Talent:

---

**Khan Mohammad Shayshab Azad**  
[LinkedIn Profile](https://linkedin.com/in/shayshab-azad) | [GitHub](https://github.com/shayshab)  
Phone: +49 15750613186 | Email: km.shayshab@gmail.com  
Location: Berlin, Germany

---

**Subject:** Application for Head of Influencer Marketing and Partnerships

Dear Jack Brawn,

I am excited to submit my application for the Head of Influencer Marketing and Partnerships position at Zazu Digital Talent. With a robust background in IT and cybersecurity, alongside demonstrated leadership capabilities, I am eager to pivot into a dynamic role that combines my technical acumen with strategic marketing initiatives in the health and wellness space.

**Relevant Skills and Experience:**

1. **Strategic Vision and Leadership:** At Deutsche Börse, I led risk management initiatives aligned with industry standards like ISO 27001, which required innovative strategic thinking and cross-department collaboration. My experience in managing strategic initiatives ensures I can effectively drive and mentor a high-performing influencer marketing team.

2. **Data-Driven Approach:** My experience in cybersecurity has ingrained a data-centric mindset, crucial for developing KPIs and leveraging analytics to optimize performance. I have successfully executed data-driven strategies to mitigate IT risks and enhance system performance, demonstrating my commitment to using data for impactful decision-making.

3. **Project Management with Large Budgets:** I have managed complex projects, ensuring resources are efficiently allocated to maximize outcomes. My role in projects like ISO 27001 compliance involved budget management and strategic resource allocation, skills that are highly transferable to managing substantial marketing budgets.

4. **Passion for Health and Wellness:** Although my professional experience is rooted in IT, I have a passionate commitment to personal health and wellness. This personal connection fuels my enthusiasm for harnessing influencer marketing to transform lives and promote well-being on a broader scale.

5. **Fluency in English and Working Knowledge of German:** I possess a high proficiency in English (C1) and am actively improving my German (A2), enabling me to thrive in international markets and support diverse teams.

I am particularly drawn to your vision of building long-term advocacy through innovative content and partnership initiatives. I am eager to bring my technical diligence and strategic insight to your team to drive meaningful brand engagement in the health and wellness sector.

I welcome the opportunity to discuss how my background, skills, and enthusiasms align with the goals of Zazu Digital Talent. Please find my CV attached for further details. Thank you for considering my application.

Warm regards,

Khan Mohammad Shayshab Azad

---

Make sure to tailor the actual CV preparing part for this specific role if you decide to proceed, highlighting any relevant experiences or skills that align with the job description, including applicable certifications or training that demonstrate your readiness for this role.