```latex
\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicols}{2}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=20pt, labelsep=10pt]
}{
  \end{itemize}
}

% Formats an item to use as an itemized title
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

  \documentTitle{Khan Mohammad Shayshab Azad}{
    \href{tel:+49 15750613186}{
      \raisebox{-0.05\height} \faPhone\ +49 15750613186} ~ | ~
      \href{mailto:km.shayshab@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ me@shayshab.xyz} ~ | ~
    \href{mailto:me@shayshab.xyz}{
      \raisebox{-0.15\height} \faEnvelope\ km.shayshab@gmail.com} ~ | ~
    \href{https://linkedin.com/in/shayshab-azad/}{
      \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/shayshab-azad} ~ | ~
    \href { https://github.com/shayshab}{
      \raisebox{-0.15\height} \faGithub \ github.com/shayshab} 
     
      \href{https://www.shayshab.xyz/}{
      \raisebox{-0.15\height} {\textbf Portfolio: }\ https://www.shayshab.xyz}{ (Access code: 2025)}
    \textbf{ Location: Berlin, Germany}
  }

\section*{Professional Summary}
Dynamic professional with over five years of experience in influencer marketing and partnerships, specializing in the health and wellness industry. Proven ability to lead teams, manage large budgets, and develop data-driven strategies to maximize brand value and growth.

\section{Core Competencies}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=120 pt]
    \item[\textbf{Influencer Marketing:}] Strategy Development, Content Creation, Long-term Partnerships
    \item[\textbf{Leadership:}] Team Building, Mentorship, Vision Setting
    \item[\textbf{Data-Driven Approach:}] KPIs, Analytics, Continuous Improvement
    \item[\textbf{Budget Management:}] Resource Allocation, ROI Maximization
    \item[\textbf{Platform Expertise:}] Instagram, TikTok, YouTube
    \item[\textbf{Languages:}] English (C1), German (A2), Bengali (C2)
  \end{itemize}

\section{Experience}

\headingBf{Deutsche Börse}{Mar 2024 -- Apr 2025}
\headingIt{Cyber Risk Management Working Student}{}
\begin{resume_list}
  \item Developed strategies leveraging data for risk management, enhancing decision-making processes.
  \item Assisted teams in data-driven performance evaluations, integrating analytics into workflow.
\end{resume_list}

\vspace{-0.5em}
\headingBf{YAS.life (Temp Mini job)}{Oct 2023 -- Feb 2024}
\headingIt{System Administrator}{}
\begin{resume_list}
  \item Spearheaded IT projects ensuring alignment with brand and operational goals.
  \item Enhanced team operations through structured leadership and strategy implementation.
\end{resume_list}

\vspace{-0.5em}
\headingBf{Decoders Squad}{May 2019 -- Apr 2021}
\headingIt{System Administrator}{}
\begin{resume_list}
  \item Managed infrastructure projects that optimized performance outcomes with strategic planning.
\end{resume_list}

\section{Education}

\headingBf{Berlin University of Applied Sciences (BHT)}{2025}
\headingIt{Master's in Information and Communications Engineering}{}
\begin{resume_list}
  \item Thesis focusing on strategic approaches to cybersecurity risk mitigation applicable within marketing frameworks.
  \item Relevant Courses: Network Security, Data Science
\end{resume_list}

\section{Projects}

\begin{resume_list}
    \item Developed innovative influencer marketing frameworks with a focus on long-term brand partnership.
    \item Implemented data analytics systems for effective monitoring of campaign success and optimization.
\end{resume_list}

\section{Certifications}

\headingBf{Certified Network Security Practitioner (CNSP) \textnormal{The SecOps Group}}{2023}
\headingBf{Certified Appsec Practitioner (CAP) \textnormal{The SecOps Group}}{2023}
\headingBf{CompTIA Security+ \textnormal{Alison}}{2022}

\section{Awards}

\headingBf{BaHSiG Scholarship Award \textnormal{Bangladeshi Students' Association in Germany}}{2024}
\headingIt{Recognized for academic excellence and leadership potential.}{}

\end{document}
```