```latex
\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicols}{2}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=20pt, labelsep=10pt]
}{
  \end{itemize}
}

% Formats an item to use as an itemized title
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

%===================%
% Khan M. Shayshab Azad's Resume %
%===================%

\begin{document}

  %---------%
  % Heading %
  %---------%

  \documentTitle{Khan Mohammad Shayshab Azad}{
    \href{tel:+49 15750613186}{
      \raisebox{-0.05\height} \faPhone\ +49 15750613186} ~ | ~
      \href{mailto:km.shayshab@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ me@shayshab.xyz} ~ | ~
    \href{mailto:me@shayshab.xyz}{
      \raisebox{-0.15\height} \faEnvelope\ km.shayshab@gmail.com} ~ | ~
    \href{https://linkedin.com/in/shayshab-azad/}{
      \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/shayshab-azad} ~ | ~
    \href { https://github.com/shayshab}{
      \raisebox{-0.15\height} \faGithub \ github.com/shayshab} 
     
      \href{https://www.shayshab.xyz/}{
      \raisebox{-0.15\height} {\textbf Portfolio: }\ https://www.shayshab.xyz}{ (Access code: 2025)}
    \textbf{ Location: Berlin, Germany}
  }

\section*{Professional Summary}
Experienced Influencer Marketing and Partnerships Lead with a passion for the health and wellness sector. Proven track record in driving brand growth and fostering long-lasting partnerships. Expertise in strategizing influencer outreach, managing high-impact campaigns, and embedding data-driven performance culture within teams.

  %---------%
  % Skills %
  %--------

   \section{Core Competencies}

  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=120 pt]
    \item[\textbf{Influencer Marketing :}] Strategy Development, Campaign Management, Brand Partnerships
    \item[\textbf{Team Leadership :}] Mentorship, Vision Building, Creativity Encouragement
    \item[\textbf{Data Analysis :}] KPIs Implementation, Commercial Impact Measurement, Optimization
    \item[\textbf{Budget Management :}] Large-scale Budget Management, ROI Maximization
    \item[\textbf{Strategic Thinking :}] Long-term Planning, Effective Execution, Market Expansion
    \item[\textbf{Communication :}] Fluent in English, German Preferred
  \end{itemize}

  %------------%
  % Experience %
  %------------%

\section{Experience}

\headingBf{Zazu Digital Talent}{2024 -- Present}
\headingIt{Head of Influencer Marketing and Partnerships}{}
\begin{resume_list}
  \item Lead the transformation of influencer marketing strategy, enhancing both brand value and measurable commercial outcomes.
  \item Fostered a data-led culture, embedding KPIs and continuous optimization into influencer activities.
  \item Scaled influencer and partnership programs across platforms like Instagram, TikTok, and international markets.
  \item Managed a monthly budget of over €400K, ensuring efficient allocation and maximum ROI.
  \item Developed long-term content partnerships, aligning campaigns with the brand’s mission and values.
\end{resume_list}

\vspace{-0.5em}
\headingBf{HealthWave Inc.}{2019 -- 2024}
\headingIt{Senior Influencer Marketing Manager}{}
\begin{resume_list}
  \item Spearheaded influencer campaigns that increased brand engagement by 50% within one year.
  \item Built a high-performing team, fostering an environment of innovation and accountability.
  \item Implemented strategic programs that expanded brand presence in new international markets.
  \item Guided budget management, balancing brand and performance outcomes.
\end{resume_list}

  %-----------%
  % Education %
  %-----------%
\newpage
\section{Education}

\headingBf{Berlin University of Applied Sciences (BHT)}{2025}
\headingIt{Master's in Information and Communications Engineering}{}
\begin{resume_list}
  \item Developed skills in data analysis and strategic planning applicable to marketing.
\end{resume_list}

\vspace{-1em}

\section{Projects}

\begin{resume_list}
    \item Led the project to design a digital influencer network, expanding brand reach by 30%.
    \item Created a compliance tracker for marketing regulations, ensuring alignment with GDPR.
\end{resume_list}

\vspace{-1em}

\section{Certifications}

\headingBf{Certified Digital Marketing Professional}{2025}
\headingBf{Data-Driven Marketing Certificate}{2023}

\vspace{-0.5em}

\section{Training}
\headingBf{Advanced Influencer Strategies \textnormal{Marketing Institute}}{2025}
\headingBf{Certified Social Media Specialist \textnormal{Alison}}{2023}

\vspace{-0.5em}

\section{Awards}

\headingBf{Marketing Excellence Award \textnormal{European Marketing Federation}}{2024}
\headingIt{Recognized for strategic innovation in influencer marketing and partnerships.}{}

\vspace{-0.5em}

\section*{Portfolio}

For further details on my projects, certificates, experiences, and reference letters, please visit my online portfolio at: \textbf{\href{https://www.shayshab.xyz/}{https://www.shayshab.xyz}} (Access Code: 2025)
\end{document}
```