\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

% Define colors
\definecolor{accentColor}{HTML}{0e6e55}

% Custom formatting
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

\begin{center}
\textbf{\Large Follow-Up Email Template}
\end{center}
\vspace{1em}
{\color{accentColor}\rule{\textwidth}{1pt}}
\vspace{1em}

\textbf{Subject:} Following Up on Business Analyst Application - Khan Mohammad Shayshab Azad

\vspace{1em}

Dear Hiring Manager,

I hope this email finds you well. I am writing to follow up on my application for the Business Analyst role at Te Group, which I submitted on 2025-07-15.

I remain very interested in this opportunity and am confident that my background in data analysis and experience with strategic planning make me a strong candidate for the position.

Since submitting my application, I have completed a comprehensive data-driven project that further demonstrates my commitment to leveraging analytics for business improvements.

I would welcome the opportunity to discuss how my qualifications align with your needs. Please let me know if you require any additional information from me.

Thank you for your consideration. I look forward to hearing from you.

\vspace{1em}

Best regards,

\vspace{1em}

Khan Mohammad Shayshab Azad\\
+49 15750613186\\
me@shayshab.xyz\\
linkedin.com/in/shayshab-azad

\end{document}